---
title: "Week 10 Notes: Mapping in R"
author: "Julea Shaw"
date: "3/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#libraries we want for spatial mapping
library(sf)
library(maps)
library(rgdal)
library(maptools)
library(mapview)
library(leaflet)
library(tidyverse)
#Installing the development version of ggplot2 with additional features that have not been released yet (need it for geom_sf )
#install.packages("devtools")
library(devtools)
devtools::install_github("tidyverse/ggplot2")

```

####Projections and Coordinate Reference Systems (CRS)

Often difficult part of workign with spatial data

GCS = geographic coordinate systems 
based on spherical earth models 

PCS = projected coordinate system
Takes sphere and maps it onto a flat surface
Certain projections are better depending on where you are on the earth
(middle is most accurate, edges stretched)



####Point data
sf is mainly for vector based data (poly-lines, polygons, point data)

moving away from rgdal because sf is easier to work with

sf vignettes to help you learn to use


st_read to read in data
brings in everything as a dataframe and the geometry is its own geometry in a list

```{r}

df_locs<- read_csv("https://raw.githubusercontent.com/ryanpeek/mapping_in_R/master/data/hotsprings_CA.csv")


#Need to add headers to columns

df_locs <-df_locs %>% 
  set_names(nm = c("State", "Lat", "Lon", "Spring_name", "Temp_C", "Temp_F", "Area", "USGS_Quad"))

glimpse(df_locs)

#Longitude should be negative

df_locs <- df_locs %>% 
  mutate("Lon" = -Lon)

#Make temperature numberic

df_locs <- df_locs %>% 
  mutate_at(.vars = c("Temp_C", "Temp_F"), .funs = as.numeric) 

# make it spatial

df_locs_sf <- st_as_sf(df_locs, 
                       coords = c("Lon", "Lat"),# or = c(3,2) col numbers
                      remove = F,
                      crs = 4326) #coordinate reference system (numbers for each projection), This is a WGS84 GCS  
```
####Making a map
```{r}
library(mapview)
mapview(df_locs_sf)

#Crop to points in Tulare county
#install.packages("USAboundaries")
library(USAboundaries)

#us_boundaries, us_cities, us_counties, us_states

tulare <- us_counties(resolution = "low", states = "CA") %>% 
  filter(name == "Tulare")

mapview(tulare) + mapview(df_locs_sf) #layers like ggplot2


```
###intersect the hotsprings with Tulare Co

```{r}
tuls_hs <- st_intersection(df_locs_sf, tulare)
mapview(tuls_hs)
```
####ggmap backgrounds

#Making a static map
```{r}
#install.packages("ggmap")
library(ggmap)
library(viridis)

map1 <- get_map(location = c(-118.302, 36.22),#x = lon, #y = lat
               color = "bw", 
               maptype = "terrain",
               source = "google",
               zoom = 8)

ggmap(map1)+
  geom_sf(data = tuls_hs, aes(color = Temp_F), size = 3, shape = 16, inherit.aes = FALSE)+
  scale_color_viridis(option = "inferno")
  
```


####Bay Carbon Concentrations

```{r}
#install.packages("naniar")
```



